---
title: "Sta 523 - Midterm Project 2 - Fall 2021"
output: rmarkdown::html_document
runtime: shiny
---
Due Friday, December 3rd by 5:00 pm

<br/>

### Rules

Review all of the rules detailed in `README.md`, if you have any questions please direct them to myself or the TAs.

<br/>

```{r}
library(tidyverse)
library(tibble)
```


### Task 1 - Figuring out the NY Times Article Search API

```
https://api.nytimes.com/svc/search/v2/articlesearch.json?fq=(print_page:1 AND print_section:\"A\" AND document_type:\"article\")&page=0&begin_date=20180713&end_date=20180713&api-key=HrTU9A9hBqzEoCZNoSfE9utPnq4grOC5
```

* `begin_date=`20180713

* `end_date=`20180713

* `facet=`

* `facet_fields=`

* `facet_filter=`

* `fl=`

* `fq=`fq=(print_page:1 AND print_section:\"A\" AND document_type:\"article\")

* `page=`0,default(the first page)

* `q=`

* `sort=` 

<br/>    

### Task 2 - Getting data from the NY Times Article Search API

The main purpose of this task is to request the API address and get the 
corresponding dataframe. Firstly, the function verifies the input date, and then
ensure the parameters in the API address to read the Json file and get the data 
frame. Here since each request retrieves just 1 page of data, we should determine 
the total page number we need from "hits" elements in the list. If there is no 
result in the specified date, it would show a empty dataframe with column names. 
Note that since the API key will be limited ar most 10 requests/minute, the sleep 
time should be set as 6 seconds. 

```{r}
get_nyt_articles = function(year, month, day, api_key) {
  # check the length of input
  if(length(year) != 1)
    stop("Year should be length 1!")
  if(length(month) != 1)
    stop("Month should be length 1!")
  if(length(day) != 1)
    stop("Day should be length 1!")
  if(length(api_key) != 1)
    stop("Api key should be length 1!")
  # check the type of integer
  if (is.numeric(year)==TRUE & is.numeric(month)==TRUE & is.numeric(day)==TRUE & is.character(api_key)==TRUE){
    # check the input date (roughly assume the date is to 2022)
    if (year>999 & year<=2022 & day>0 & day<32){
    # check if the date is valid
    checkdate = tryCatch(lubridate::is.Date(as.Date(paste(year, month, day, sep = '-'))), 
             error = function(e) return(FALSE)) 
      if (checkdate == TRUE){
        # convert date format
        old_date = paste(month,day,year,sep = "/")
        new_date = as.character(as.Date(old_date,"%m/%d/%Y"),"%Y%m%d")
      } else{return("the date should be valid")}
    } else{return("the date should be valid")}
  } else{return("the type of input should be valid")}
  
  # combine url parameters
  nyt_url = paste0("https://api.nytimes.com/svc/search/v2/articlesearch.json?",
           "fq=(print_page:1 AND print_section:\"A\" AND document_type:\"article\")",
           "&begin_date=",new_date,"&end_date=",new_date,"&page=0&api-key=",api_key)
  # read json file 
  nytimes = jsonlite::read_json(nyt_url) 
  # get the total number of page
  hits = nytimes$response$meta$hits
  page_total = hits/10
  if (schoolmath::is.decimal(page_total) == TRUE){
  page_total = as.integer(page_total)+1
  }else{page_total = as.integer(page_total)}
  
  # get tidy data frame from current API
  nyt_all = tibble()
  page = 0
  if(hits>0){
    repeat{
      nytimes = nytimes$response$docs %>%
        tibble(data = .) %>%
        hoist(
          data,
          "headline",
          "byline",
          "web_url",
          "lead_paragraph",
          "source"
        )%>% 
        select(!any_of("data"))
      # combine all current page
      nyt_all = rbind(nyt_all,nytimes)
      
      # stop if it processing the last page
      if(page == page_total-1)
        break

      page = page + 1
      Sys.sleep(6)
      
      # get new page
      nyt_url = paste0("https://api.nytimes.com/svc/search/v2/articlesearch.json?",
           "fq=(print_page:1 AND print_section:\"A\" AND document_type:\"article\")",
           "&begin_date=",new_date,"&end_date=",new_date,"&page=",
           page,"&api-key=",api_key)
      nytimes = jsonlite::read_json(nyt_url) 
    }
  }else{
    # if no result, then empty dataset
    nyt_all = tibble(
      headline = list(head = list(main = '')),
      byline = list(byline = list(original = '')),
      web_url = '',
      lead_paragraph = '',
      source= '')  
    }
 return(nyt_all)
}
```



<br/>

### Task 3 - Shiny Front End

This app asks user to input the date and their api key to retrieve the articles 
they want from the newyork times website. The headlines would show up in the main 
panel when they hit the retrieval button. After they click the headline, 
a window would show up containing the information of the selected article 
including the byline, the first leading paragraph, as well as the url link 
to the article for further reading. The code is implemented based on 
the structure provided, and it is separated into two modules UI and Server. 
The retrieved result is purely based on the response from the get_nyt_articles 
from task 2. 
Note if there is no information in a certain date, shiny app would output a message. 

```{r}
library(shiny)
library(purrr)
library(shinyWidgets)
```

```{r}
# this function takes data retrieved from api and extract the title and byline information from it. 
extractline = function(data){
  titles = c()
  bylines= c()
  if (length(data$headline[[1]])>1){
  for ( i in 1:nrow(data)){
    title = data$headline[[i]]$main
    byline = data$byline[[i]]$original
    titles= c(titles, title)
    bylines = c(bylines, byline)
  }
  info = list("title"= titles,
              "byline" = bylines)}
  else{info = list('title' = 'Nothing is here',
                   'byline' = 'Too bad lol')}
  return(info)
}


```

```{r, ui}
# the UI module is used to set up the background, main panel and sidebars 
UI = fluidPage(
    setBackgroundImage(
    src = "https://img4.goodfon.com/wallpaper/nbig/c/da/the-new-york-times-niu-iork-taims-ssha-new-york-amerikanskai.jpg"
  ),
    titlePanel(h3("NYTimes API",
                  style = "color: white")),
    sidebarLayout(
      sidebarPanel(
        # input for links #, n ,
        br(),
        # input for dates, Date
        dateInput("Date",
                  "Date to look at",
                  value = "2018-07-13",
                  format = "yyyy-mm-dd",
                  startview = "month",
                  weekstart = 0, 
                  language = "en"),
        br(),
        textInput("Key",
                  "Your API key", 
                  value = "HrTU9A9hBqzEoCZNoSfE9utPnq4grOC5"),
        
        br(),
        actionButton("Retrieve","Retrieve !!!")
      ),
      mainPanel(
        uiOutput("Headlines")
        )
    )
  )

```

```{r, server}
# This server module is responsible for reacting to any clicks and information a user put into the side bar 
# and return corresponding information in the mainpanel and modal box 

SERVER = function(input, output, session) {
    state = reactiveValues(
      observers = list()
    )
    # observe retrieve 
    observeEvent(input$Retrieve, {
      # Destroy existing observers
      for(i in seq_along(state$observers)) {
        state$observers[[i]]$destroy()
      }
      # retrieve the necessary information 
      key = input$Key
      date = as.character(input$Date)
      date_list = strsplit(date, "-")
      year = date_list[[1]][1]
      year = as.integer(year)
      month = date_list[[1]][2]
      month = as.integer(month)
      day = date_list[[1]][3]
      day = as.integer(day)
      data = get_nyt_articles(year, month, day, key)
      n = nrow(data)
      information = extractline(data)
      headline = information[["title"]]
      byline = information[["byline"]]
      links = data$web_url
      leadparagraph = data$lead_paragraph
      # Destroy existing observers
      for(i in seq_along(state$observers)) {
        state$observers[[i]]$destroy()
      }
        
      ui_elems = map(
        seq_len(n), 
        function(i) 
          fluidRow(actionLink(paste0("Headlines",i), 
                              h4(headline[i]),
                              style="color: white"))
      )
      
      output$Headlines = renderUI(fluidPage(ui_elems))
      # Reset and create new observers for each of our links
      state$observers = map(
        seq_len(n), 
        function(i) {
          label = paste0("Headlines",i)
          observeEvent(input[[label]], ignoreInit = TRUE, {
               showModal(modalDialog(title = headline[i],
                 byline[i],
                 h5("First Paragraph:"),
                 leadparagraph[i],
                 h5("Link:"),
                 # for linking to the webpage
                 a(href = links[i],links[i]),
                 size = "l"
                 )
                 )
          })
        }
      )
    })
  }

```


```{r}
shinyApp(
  ui = UI,
  server = SERVER
)
```

